Verifying Demonstrations

### 2018-10-31 paper/privacy-properties.tex
added caveat about threshold, edited blockchain cost in discussion

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against 
her will.
Receipt freeness, while desirable, is not \emph{always} desirable.
For instance, the location proof might be useful to prove presence to a third 
party, \eg for strengthening the authenticity of witness information.

@@

For the witness, we want unlinkability between a witness's identity \(W\) and a 
location \(l\) against an adversary who is not present in the location.
Due to the limitations of physical space, two individuals present in the same 
location will inevitably learn of each other's presence.
Thus we will only try to prevent individuals who are not present to learn of 
this presence.

\sonja{new}
Difference to e-voting:
physical presence means support for a cause if there is one protest. If there is a counterprotest, physical presence with that group means support for the counterprotest. In our system, it gets more ambiguous as the participants are counted if all of the following is true
\begin{enumerate*}
\item they participate in the protocol,
\item they use the protest identifier (cause) for which the count is done,
\item they meet the eligibility criteria, and
\item they receive enough proof shares,
\item that are uploaded to the ledger.
\end{enumerate*}
Thus one could participate in a protest and be counted even when physically 
present at a counter-protest if the two protests are co-located and the 
participant chooses the corresponding cause/identifier of the original protest.

@@

 \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
     too of course} unless the witness discloses the receipt (by revealing her 
   identity), there is no link between the protest data on the ledger and the 
   identity of the witness.
\end{description}
\sonja{old}
In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).

As a consequence, this leaves us with with what would correspond to vote privacy.
In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
Moreover, any temporary identifiers such as pseudonyms may only be
reused when strictly necessary for the fulfillment of verifiability
properties listed in \label{verifiability-properties} to prevent
inference on long-term identities by repeated samples and side information.

>>>>

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against 
her will.
Receipt freeness, while desirable at first glance, is not desirable
here as, in contrast to voting, receipt freeness for \emph{how} the
voter voted (\ie the cause of the protest) implies receipt freeness
for \emph{that} the voter voted (\ie the protester was there) which
conflicts with verifiability.  
%For instance, the location proof might be useful to prove presence to a third 
%party, \eg for strengthening the authenticity of witness information.

@@

\sonja{removed for now: For the witness, we want unlinkability between a witness's identity \(W\) and a 
location \(l\) against an adversary who is not present in the location.
Due to the limitations of physical space, two individuals present in the same 
location will inevitably learn of each other's presence.
Thus we will only try to prevent individuals who are not present to learn of 
this presence.}

\sonja{start of older thoughts}
Difference to e-voting:
physical presence means support for a cause if there is one protest. If there is a counterprotest, physical presence with that group means support for the counterprotest. In our system, it gets more ambiguous as the participants are counted if all of the following is true
\begin{enumerate*}
\item they participate in the protocol,
\item they use the protest identifier (cause) for which the count is done,
\item they meet the eligibility criteria, and
\item they receive enough proof shares,
\item that are uploaded to the ledger.
\end{enumerate*}
Thus one could participate in a protest and be counted even when physically 
present at a counter-protest if the two protests are co-located and the 
participant chooses the corresponding cause/identifier of the original protest.

@@

 \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
     too of course} unless the witness discloses the receipt (by revealing her 
   identity), there is no link between the protest data on the ledger and the 
   identity of the witness.
\end{description}

In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).

As a consequence, this leaves us with with what would correspond to vote privacy.
In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
\sonja{end older thoughts}
Moreover, any temporary identifiers such as pseudonyms may only be
reused when strictly necessary for the fulfillment of verifiability
properties listed in \label{verifiability-properties} to prevent
inference on long-term identities by repeated samples and side information.
